Viscous Transport in Eroding Porous Media

### 2019-10-03 docs/transport/erosion_transport.tex
looked at last two comments. Have sent a few figure updates to S-H

In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
function of the porosity. The initial porosity is $\phi = 37.68\%$, and
the initial tortuosity is $T = 1.16$.  The tortuosity is computed with
both the length of the streamlines~\eqref{eqn:tortuosity1} (red stars)
and using the spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
The two tortuosity formulas give similar results, and any discrepancy
can be accounted for by slow regions of recirculation and from applying
quadrature to compute the tortuosity.  As the bodies erode, wide
channels form where streamlines undergo only minor vertical deflections,
and this explains why the tortuosity eventually decreases with porosity.
We computed lines of best fit using the porosity-tortuosity
models~\eqref{eqn:tortuosityModels} and found the power law to give the
smallest error.  The  black dashed line in
Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.2064}
\end{align}
with a root-mean-square error of $5.90 \times 10^{-3}$.  Interestingly,
at the low porosities, the tortuosity initially increases. This increase
occurs because in the absence of erosion (left plot in
Figure~\ref{fig:Eroding20vort}), many of the streamlines, such as those
initialized between bodies 15 \& 18, only perform minor deflections to
pass through the narrow regions, albeit, very slowly.  However, as
erosion starts to open the channels, the streamlines deflect into the
fast regions, such as the region above body 11, and this increases the
amount of vertical deflection, and therefore the tortuosity.

\todo[inline]{I wonder if this initial increase in the tortuosity is specific to the process of erosion, or if it would also occur if we simply took a collection of circular bodies and changed the porosity by controlling the radii? We don't have to answer this question now, but it would be interesting to consider in the future.}

>>>>

In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
function of the porosity. The initial porosity is $\phi = 37.68\%$, and
the initial tortuosity is $T = 1.16$.  The tortuosity is computed with
both the length of the streamlines~\eqref{eqn:tortuosity1} (red stars)
and using the spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
The two tortuosity formulas give similar results, and any discrepancy
can be accounted for by slow regions of recirculation and from applying
quadrature to compute the tortuosity.  As the bodies erode, wide
channels form where streamlines undergo only minor vertical deflections,
and this explains why the tortuosity eventually decreases with porosity.
We computed lines of best fit using the porosity-tortuosity
models~\eqref{eqn:tortuosityModels} and found the power law to give the
smallest error.  The  black dashed line in
Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.2064}
\end{align}
with a root-mean-square error of $5.90 \times 10^{-3}$.  Interestingly,
at the low porosities, the tortuosity initially increases. This increase
occurs because in the absence of erosion (left plot in
Figure~\ref{fig:Eroding20vort}), many of the streamlines, such as those
initialized between bodies 15 \& 18, only perform minor deflections to
pass through the narrow regions, albeit, very slowly.  However, as
erosion starts to open the channels, the streamlines deflect into the
fast regions, such as the region above body 11, and this increases the
amount of vertical deflection, and therefore the tortuosity. While this
increase in tortuosity is interesting, in the next two examples we will
see that the tortuosity does not initially increase.
